---
title: "Course Summary"
author: "Paul May"
date: "October 21, 2016"
output: html_document
---

## Day 1: Packages and Version Control

Learned to create a package using [devtools][1].  The way to get started is 
to create the skeleton of a package.
```
library(devtools)
create("Paul")
```

This creates a directory with a couple of files and a folder.
We then did the following:

1. The DESCRIPTION contains info about the package; we edited it for our purposes.
2. Looked an NAMESPACE file, didn't touch it.
3. Created first function in R folder, `hi()`.

We then used [roxygen2][] to add documentation to the function, including
information about parameters and return values.
Also used tags (`@export`) to indicate that we wanted to 'export' the function 
from the namespace. 

We also learned to manage our source code using [github][].

Here's the result of our work:

```{r our-package}
library(Paul)
hi("Paul")
```

##Day 2: Classis, Tidy and Rich Data

'Classic' data is represented as a `data.frame()` with samples and rows and 
features as columns.

```{r}
pdatafl = "C:\\Users\\May_CA\\Desktop\\R Workshop\\Data Sets\\All-phenoData.csv"
exprfl = "C:\\Users\\May_CA\\Desktop\\R Workshop\\Data Sets\\All-expression.csv"
classic = input_classic(pdatafl, exprfl)
classic[1:5, c(1:3, 22:25)]

```

One of the things we did was plot the distribution of expression values
across genes

```{r clasic-exprs-hist}
hist(colMeans(classic[, -(1:22)]))
```







[1]: https://cran.r-project.org/package=devtools
[roxygen2]: https://cran.r-project.org/package=roxygen2
[github]: https://github.com
